Automatic Identification and Annotation of Parallel Tasks in Structured Programs

### 2018-01-11 docs/ACM/paper.tex

>>>>

\begin{figure}[t!]
\begin{center}
\includegraphics[width=0.9\columnwidth]{images/Absolute_speedups}
\caption{Speedup comparisons -- automatic annotations compare favourably against
manual interventions, and lead to great performance gains.
The Y-axis shows the speedup of either manual intervention, or automatic
annotation (this paper) onto the original programs.}
\label{fig:Absolute_speedups}
\end{center}
\end{figure}

\begin{figure}[t!]
\begin{center}
\includegraphics[width=0.9\columnwidth]{images/Opt_Speedups}
\caption{The benefit of our optimizations.
Each optimization (profitability analysis and recursion bounds) lead to
non-trivial speedups.}
\label{fig:Opt_Speedups}
\end{center}
\end{figure}
